Scalar and Representative Observables, and Their Associated Statistical Model, for Polarimetric SAR Data

### 2014-11-22 paper_dev/article.tex
auto

%\author{Thanh-Hai Le, Ian McLoughlin}
\author{Thanh-Hai~Le,
        Ian~Vince~McLoughlin, 
	and Chan-Hua~Vun%
\thanks{Thanh-Hai~Le and Chan-Hua~Vun are with School of Computer Engineering, 
Nanyang Technological University, Singapore. Ian~McLoughlin is with the School of Information Science and Technology,
University of Science and Technology of China.
}% <-this % stops a space
%\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS Innovation-Works Singapore for 
%	providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
\thanks{Manuscript received March, 2014; revised March, 2014.}}

\markboth{IEEE Journal on Selected Topics in Applied Earth Observation and Remote Sensing,~Vol.~x, No.~x, x~2014}%
{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Observables, and Their Associated Statistical Model, for Polarimetric SAR Data}

>>>>

%\author{Thanh-Hai Le, Ian McLoughlin}
\author{Thanh-Hai~Le,
        Ian~Vince~McLoughlin, 
	and Chan-Hua~Vun%
\thanks{Thanh-Hai~Le and Chan-Hua~Vun are with School of Computer Engineering, 
Nanyang Technological University, Singapore. Ian~McLoughlin is with the School of Information Science and Technology,
University of Science and Technology of China.
}% <-this % stops a space
%\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS Innovation-Works Singapore for 
%	providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
\thanks{Manuscript received November, 2014; revised ????, 2015.}}

\markboth{IEEE Geoscience and Remote Sensing Letters,~Vol.~x, No.~x, x~2015}%
{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Observables, and Their Associated Statistical Model, for Polarimetric SAR Data}
